---
title: "COMPSCIX 415.2 Homework 7"
author: "Mario Casas Gonzalez"
date: "July 24, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

My Github repository for my assignments can be found at this URL: https://github.com/casasgmario/compscix-415-2-assignments 

```{r load_packages, warning=FALSE, message=FALSE}
library(mdsr)
library(tidyverse)
library (readr)
```

###Exercise 1 - Load the train.csv dataset into R. How many observations and columns are there?

There is 1,460 observation and 81 variables i.e. columns in the 'train.csv' dataset. 

```{r Exercise1, warning=FALSE, ECHO=TRUE}
train_dataset <- read_csv('C:/Users/mcgonzalez/Documents/Training/Berkeley/COMPSCI X415.2 - 002 Introduction to Data Science/Session 7 Homework/train.csv')
glimpse(train_dataset)

```

###Exercise 2

####• Visualize the distribution of SalePrice.
####• Visualize the covariation between SalePrice and Neighborhood.
####• Visualize the covariation between SalePrice and OverallQual.


```{r Exercise2}
train_dataset %>% ggplot(aes(x=SalePrice))+geom_histogram(binwidth = 10000)

```


Question 2 - Unique region values extracted: 

 [1] "Europe/Andorra"                 "Asia/Dubai"                    
 [3] "Asia/Kabul"                     "America/Antigua"               
 [5] "America/Anguilla"               "Europe/Tirane"                 
 [7] "Asia/Yerevan"                   "Africa/Luanda"                 
 [9] "America/Argentina/Buenos_Aires" "America/Argentina/Cordoba"     
[11] "America/Argentina/Salta"        "America/Argentina/Tucuman"     
[13] "America/Argentina/San_Juan"   


```{r Extract Data the tidy way}
country_col <- select(WorldCities, country)
country_col <- WorldCities %>% select(country)
WorldCities %>% select(country) %>% unique()

```

Question 3 - Unique country codes extracted:

1        AD
3        AE
15       AF
65       AG
66       AI
67       AL
87       AM
104      AO
131      AR

```{r Visualize it}

WorldCities %>% ggplot(aes(x = population)) + geom_histogram()
WorldCities %>% ggplot(aes(x = population)) + geom_histogram() + xlab('City Population')
WorldCities %>% ggplot(aes(x = population)) + geom_histogram() + 
  xlab('# People') + ylab ('# Cities') + ggtitle('My Question 4 Histogram')


```


QUestion 4 - plot generated above


