---
title: "Homework-Week-2"
author: "Mario Casas Gonzalez"
date: "June 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

Exercises

1. Run ggplot(data = mpg). What do you see?:

```{r 3.2.4 Exercise 1, include=TRUE, warning=FALSE, message=FALSE}
library (tidyverse)
library (mdsr)
ggplot(data = mpg)

```


2. How many rows are in mpg? How many columns? >> 234 rows (Observations), 11 columns (Variables)

```{r 3.2.4 Exercise 2, include=TRUE, warning=FALSE, message=FALSE}

View (mpg)

```

3. What does the drv variable describe? Read the help for ?mpg to find out. >> It's a variable to determine the type of car i.e. f = front-wheel drive, r = rear wheel drive, 4 = 4wd


```{r 3.2.4 Exercise 3, include=TRUE, warning=FALSE, message=FALSE}

?mpg

```

4. Make a scatterplot of hwy vs cyl.


```{r 3.2.4 Exercise 4, include=TRUE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=hwy,y=cyl))


```

5. What happens if you make a scatterplot of class vs drv? Why is the plot not useful? >> Because 


```{r 3.2.4 Exercise 5, include=TRUE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=class,y=drv))


```

3.3.1 

Q1> What's wrong with this code? Why are the points not blue? >> Because in order to set an aesthetic, you have to set it by name as an argument of the geom function and outside of the aes() 

```{r 3.3.1 Exercise 1, include=TRUE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=displ, y=hwy), color="blue")


```

Q2> Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg? 

Categorical: manufacturer, model, trans, drv, fl, class
Continuous: displ, year, cyl, cty, hwy 
You can tell by looking at the description of the variables and associated values. 


Q3> Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables? 

You cannot map a continuous variable to shape. 


```{r 3.3.1 Question 3, include=TRUE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=displ, y=hwy, color=displ))
ggplot (dat = mpg) + geom_point(mapping=aes(x=displ, y=hwy, size=displ))

```

Q4> What happens if you map the same variable to multiple aesthetics?

What happens is that all aesthetics after the first one do not add any extra information to the plot. 

```{r 3.3.1 Question 4, include=TRUE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=cyl, y=hwy, color=displ, size=displ))

```

Q5> What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

```{r 3.3.1 Question 5, include=TRUE, warning=FALSE, message=FALSE}



```


What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)?



Look at the data graphics at the following link: What is a Data Scientist. Please briefly critique the designer’s choices. What works? What doesn’t work? What would you have done differently? 

```{r 3.3.1 Exercise 5, include=TRUE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=class,y=drv))


```

