---
title: "COMPSCIX 415.2 Homework 7"
author: "Mario Casas Gonzalez"
date: "July 24, 2018"
output: 
  html_document:
    toc: TRUE
    theme: united 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_packages, warning=FALSE, message=FALSE}
library(mdsr)
library(tidyverse)
library (readr)
library(broom)
```

###Exercise 1 

####Load the train.csv dataset into R. How many observations and columns are there?

There is 1,460 observation and 81 variables i.e. columns in the 'train.csv' dataset. 

```{r Exercise1, warning=FALSE, ECHO=TRUE}
train_dataset <- read_csv('C:/Users/mcgonzalez/Documents/Training/Berkeley/COMPSCI X415.2 - 002 Introduction to Data Science/Session 7 Homework/train.csv')
glimpse(train_dataset)

```

###Exercise 2

####• Visualize the distribution of SalePrice.
####• Visualize the covariation between SalePrice and Neighborhood.
####• Visualize the covariation between SalePrice and OverallQual.


```{r Exercise2, ECHO='TRUE'}
train_dataset %>% ggplot(aes(x=SalePrice))+geom_histogram(binwidth = 10000)
traindataset_Neighborhood_lm <- lm(SalePrice ~ Neighborhood, data = train_dataset)
tidy(traindataset_Neighborhood_lm)
train_dataset %>% ggplot () + geom_boxplot(aes(x=reorder(Neighborhood,SalePrice),y=SalePrice)) + xlab('Neighborhood')
train_dataset %>% ggplot () + geom_boxplot(aes(x=reorder(OverallQual,SalePrice),y=SalePrice)) + xlab('OverallQual')


```

### Exercise 3

#####• take a look at the coefficient,
#####• compare the coefficient to the average value of SalePrice, and
#####• take a look at the R-squared.

The coefficient for Sale Price versus Overall Quality are Intercept -96206, and 45,436. 

The average of Sale Price is 180,921. 

R squared is 0.626. 


```{r ECHO='TRUE'}
lm(formula=SalePrice ~ OverallQual, data = train_dataset)
SalePrice <- train_dataset$SalePrice
mean(SalePrice)
glance(lm(formula=SalePrice ~ OverallQual, data = train_dataset))

```


### Exercise 4

• What kind of relationship will these features have with our target? 
  
  -'GrLivArea' shows living area square feet so should have a positive correlation with the Sale Price. Same thing should happen with 'OverallQual' as this variable is an indication of the overall material and finish quality.  
  
• Can the relationship be estimated linearly?

  They should be. 

• Are these good features, given the problem we are trying to solve?

 I would say the living space size and overall quality should be helpful in predicting the Sale Price. The p value shown below is low. 

```{r}
lm(formula=SalePrice ~ GrLivArea + OverallQual + Neighborhood, data=train_dataset) %>% tidy()
lm(formula=SalePrice ~ GrLivArea + OverallQual + Neighborhood, data=train_dataset) %>% glance()


```


• How would you interpret the coefficients on GrLivArea and OverallQual? 

They mean for every relative unit we increase the living space or the Overall Quality, the price of the house would increase by 55.56 and 20,951 respectively.  

• How would you interpret the coefficient on NeighborhoodBrkSide?

It means that, comparatively, when leaving the other 2 factors living space and overall quality constant, the price of the house is lower on this neighborhood than the avarage across the city.   

• Are the features significant? • Are the features practically significant?

These features seem to have a practical correlation with the Sale Price, and this is also proved by the low P. value.  

• Is the model a good fit?

As indicated by R squared adjusted of 0.783, Yes.  

### Exercise 6

```{r Exercise6, ECHO='TRUE'}

sim1a <- tibble(x = rep(1:10, each = 3), y = x * 1.5 + 6 + rt(length(x), df = 2))
sim1a_lm <- lm(formula= y ~ x, data=sim1a)
lm_x <- lm(formula= y ~ x, data=sim1a)
glance(lm_x)

```

What do you notice about the model’s coefficient on x and the R-squared values? 

The rsquared values vary widely for different runs of the code, even though the x value seems to remain around the 1.4 mark. 





