---
title: "COMPSCIX 415.2 Homework 1"
author: "Mario Casas Gonzalez"
date: "June 9, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

My Github repository for my assignments can be found at this URL: https://github.com/casasgmario/compscix-415-2-assignments 

```{r load_packages, warning=FALSE, message=FALSE}
library(mdsr)
library(tidyverse)
data("WorldCities")
glimpse(WorldCities)
```

Question 1 - Ther is 23018 observations of 10 variables, some of the variables are longitude, latitude, population, etc. 


```{r Extract Parts of the data}
View (WorldCities)
WorldCities <- head(WorldCities, 200) # 200 rows
country_col <- WorldCities$country
unique(country_col)
country_reg <- WorldCities$region
unique(country_reg)
```


Question 2 - Unique region values extracted: 

 [1] "Europe/Andorra"                 "Asia/Dubai"                    
 [3] "Asia/Kabul"                     "America/Antigua"               
 [5] "America/Anguilla"               "Europe/Tirane"                 
 [7] "Asia/Yerevan"                   "Africa/Luanda"                 
 [9] "America/Argentina/Buenos_Aires" "America/Argentina/Cordoba"     
[11] "America/Argentina/Salta"        "America/Argentina/Tucuman"     
[13] "America/Argentina/San_Juan"   


