---
title: "Homework-Week-2"
author: "Mario Casas Gonzalez"
date: "June 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

Section 3.2.4 - All Exercises

Q1> Run ggplot(data = mpg). What do you see?. 

>> No plot is shown. 

```{r 3.2.4 Exercise 1, include=TRUE, warning=FALSE, message=FALSE}
library (tidyverse)
library (mdsr)
ggplot(data = mpg)

```


Q2> How many rows are in mpg? How many columns? 

>> 234 rows (Observations), 11 columns (Variables)

```{r 3.2.4 Exercise 2, include=TRUE, warning=FALSE, message=FALSE}

View (mpg)

```

Q3> What does the drv variable describe? Read the help for ?mpg to find out. 

>> It's a variable to determine the type of car i.e. f = front-wheel drive, r = rear wheel drive, 4 = 4wd



```{r 3.2.4 Exercise 3, include=TRUE, warning=FALSE, message=FALSE}

?mpg

```

4. Make a scatterplot of hwy vs cyl.


```{r 3.2.4 Exercise 4, include=TRUE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=cyl,y=hwy))


```

Q5. What happens if you make a scatterplot of class vs drv? Why is the plot not useful? 

>> Because the same information is better represented through a table rather than a plot. 


```{r 3.2.4 Exercise 5, include=TRUE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=class,y=drv))


```

Section 3.3.1 All Exercises 

Q1> What's wrong with this code? Why are the points not blue? >> Because in order to set an aesthetic, you have to set it by name as an argument of the geom function and outside of the aes() 

```{r 3.3.1 Exercise 1, include=TRUE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=displ, y=hwy), color="blue")


```

Q2> Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg? 

Categorical: manufacturer, model, trans, drv, fl, class
Continuous: displ, year, cyl, cty, hwy 
You can tell by looking at the description of the variables and associated values. 


Q3> Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables? 

You cannot map a continuous variable to "shape", which is intended to represent categorical variables.  


```{r 3.3.1 Question 3, include=TRUE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=displ, y=hwy, color=displ))
ggplot (dat = mpg) + geom_point(mapping=aes(x=displ, y=hwy, size=displ))

```

Q4> What happens if you map the same variable to multiple aesthetics?

What happens is that all aesthetics after the first one do not add any extra information to the plot. 

```{r 3.3.1 Question 4, include=TRUE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=cyl, y=hwy, color=displ, size=displ))

```

Q5> What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)? 

>> The stroke aesthetic modifies the width of the shape border. It works with numeric arguments.  

```{r 3.3.1 Question 5, include=TRUE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=hwy, y=class))
ggplot (dat = mpg) + geom_point(mapping=aes(x=hwy, y=class, stroke=cyl))

```


Q6> What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)?

>> What happens is the aesthetic displays a binary value (in this case orange or blue) as a result of evaluating the condition.   

```{r 3.3.1 Question 6, include=TRUE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=hwy, y=class, colour=displ<5))


```


Section 3.5.1: Exercises #4 and #5 only

Exercise #4 > What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?

>> The advantages include having a better visual representation and screen space usage of how the first 2 variables behave as we change the third variable for comparison purposes, in this case the car class. The disadvantages include having multiple panels to extract insights. As the dataset grows, the number of panels generated through faceting may become unmanageable. 

```{r 3.5.1 Exercise #4, include=FALSE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=displ, y=hwy)) + facet_wrap(~ class, nrow = 2)

```

Exercise #5 > Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol argument?

>> 'nrow' is an argument that determines the number of rows wher the various panels get represented. 'ncol' determines the number of columns for the same purpose. 'facet_grid' forms a matrix of panels defined by row and column facetting variables, all on a single row of panels hence 'nrow' and 'ncol' are not required. 

```{r 3.5.1 Exercise 5, include=TRUE, warning=FALSE, message=FALSE}

ggplot (dat = mpg) + geom_point(mapping=aes(x=displ, y=hwy)) + facet_grid(~ class)

```


Section 3.6.1: #1-5. Extra Credit: Do #6

Exercise #1 What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?

>> 'Geom_Smooth' for a Line chart.  'geom_boxplot' for a boxplot. 'geom_histogram' for a histogram. 

```{r 3.6.1 Exercise 1, include=TRUE, warning=FALSE, message=FALSE}

ggplot (data = mpg) + geom_smooth(mapping=aes(x=displ, y=hwy, linetype = "drv"))


```


Exercise #2 Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.

```{r 3.6.1 Exercise 2, include=TRUE, warning=FALSE, message=FALSE}

ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
geom_point() + 
geom_smooth(se = FALSE)

```


Exercise #3 What does show.legend = FALSE do? What happens if you remove it?
Why do you think I used it earlier in the chapter?

>> It should remove the legend from the side of the plot. If you remove it then it should show the legend again. You used earlier for consistency with the 2 other panels shown on that particular plot.  

```{r 3.6.1 Exercise 3, include=TRUE, warning=FALSE, message=FALSE}

ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv), show.legend = FALSE) + 
geom_point() + 
geom_smooth(se = FALSE)

```

Exercise #4 What does the se argument to geom_smooth() do?

>> It displays confidence interval around smooth, as explained in the ?geom_smooth help command. 

Exercise #5 Will these two graphs look different? Why/why not?

>> They look the same because geom_point and geom_smooth both inherit the attributes of the ggplot. 

```{r 3.6.1 Exercise 5, include=TRUE, warning=FALSE, message=FALSE}

ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))

```


Exercise #6 Recreate the R code necessary to generate the following graphs.


Section 3.7.1 

Exercise #2 What does geom_col() do? How is it different to geom_bar()?

>> 'geom_col()' generates a bar chart where the heights of the bars represent values in the data. 'geom_bar()' makes the height of the bar proportional to the number of cases or the sum of the weights in each group.  

Final Question - Look at the data graphics at the following link: What is a Data Scientist. Please briefly critique the designer’s choices. What works? What doesn’t work? What would you have done differently? 

The designer uses a combination of pie charts, histograms and bubbles, somewhat lacking consistency for the reader. 

In my view the information given on the pie charts e.g. % of Data Scientist Demand may have a better visual impact through a histogram. Also the colour code should have been included in the legend. 

Colour coding in general could be improved, as an example the 3rd section seems to imply a darker blue means a higher % but there is no legend to show that. 

The multiple panels on the 4th section could be replaced fro a more compact view through single panel with colour coding. Same applies to the second to the last plot. 

The last section shows all % figures with the same height. I would have weighted the height based on % for better visualization.   



