---
title: "Homework-Week-2"
author: "Mario Casas Gonzalez"
date: "June 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

Exercises

1. Run ggplot(data = mpg). What do you see?:

```{r 3.2.4 Exercise 1, include=FALSE, warning=FALSE, message=FALSE}
library (tidyverse)
library (mdsr)
ggplot(data = mpg)

```


2. How many rows are in mpg? How many columns? >> 234 rows (Observations), 11 columns (Variables)

```{r 3.2.4 Exercise 2, include=FALSE, warning=FALSE, message=FALSE}

View (mpg)

```

3. What does the drv variable describe? Read the help for ?mpg to find out. >> It's a variable to determine the type of car i.e. f = front-wheel drive, r = rear wheel drive, 4 = 4wd


```{r 3.2.4 Exercise 3, include=FALSE, warning=FALSE, message=FALSE}

?mpg

```

4. Make a scatterplot of hwy vs cyl.


```{r 3.2.4 Exercise 4, include=FALSE, warning=FALSE, message=FALSE}

?mpg

```

5. What happens if you make a scatterplot of class vs drv? Why is the plot not useful?


```{r 3.2.4 Exercise 5, include=FALSE, warning=FALSE, message=FALSE}

?mpg

```
