---
title: "COMPSCIX 415.2 Homework 3"
author: "Mario Casas Gonzalez"
date: "June 24, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


My Github repository for my assignments can be found at this URL: https://github.com/casasgmario/compscix-415-2-assignments 

```{r load_packages, warning=FALSE, message=FALSE}
library(mdsr)
library(tidyverse)
library(nycflights13)

```

SECTION 3.8.1 ALL EXERCISES

Question 1 - What is the problem with this plot? How could you improve it? 

>> The problem with it is overplotting. You can improve it by using the position adjustment "jitter". This adds certain randomness to the values, which results in spreading multiple points with the same value out. 


```{r Section 3.8.1 Question 1}

ggplot (data=mpg, mapping= aes (x=cty, y = hwy)) + geom_point()
ggplot (data=mpg, mapping= aes (x=cty, y = hwy)) + geom_point() + geom_jitter()


```


Question 2 - What parameters of geom_jitter() control the amount of jittering?

>>'width' and 'height' control the amount of horizontal and vertical jitter. 


```{r Section 3.8.1 Question 2}

?geom_jitter


```

Question 3 - Compare and contrast geom_jitter() with geom_count()

>> geom_cout() counts the number of observations at each location, then maps the count to point area. 

```{r Section 3.8.1 Question 3}

?geom_count
ggplot (data=mpg, mapping= aes (x=cty, y = hwy)) + geom_point() + geom_jitter()
ggplot (data=mpg, mapping= aes (x=cty, y = hwy)) + geom_point() + geom_count()

```


Question 4 - What's the default position for geom_boxplot()? Create a visualisation of the mpg dataset that demonstrate it. 

>> The default position is Identity. 

```{r Section 3.8.1 Question 4}

ggplot (data=mpg) + geom_boxplot(mapping = aes (x=class, y=hwy))

```


SECTION 3.9.1 

Exercise #2 - What does "labs()" do?. Read the documentation. 

>> Labs() allows you to set axis labels as well as titles and subtitles to provide information about the data source. 


Exercise #4 - What does the plot below tell you about the relationship between city and highway mpg? Why is 'coord_fixed()' important? What does 'geom_abline()' do?

>> It tells us that there is a direct relationship between mpg driving at cities and highways, as expected. 
'coord_fixed()' forces a specified ratio between the physical representation of data units on the axes, and it is important because it can be used to alter the visualization for the reader, improve their visual perception or even manipulate the interpretation.   
'geom_abline()' adds reference lines (sometimes called rules) to a plot, either horizontal, vertical, or diagonal (specified by slope and intercept). These are useful for annotating plots.

```{r Section 3.9.1 Question 4}

ggplot(data = mpg, mapping = aes (x= cty, y = hwy)) + geom_point() + geom_abline() + coord_fixed()
ggplot(data = mpg, mapping = aes (x= cty, y = hwy)) + geom_point() + geom_abline() + coord_fixed(ratio = 2)


```


SECTION 4.4 | EXERCISES #1 AND #2 

Exercise # 1 - Why does this code not work? >> Because the point in the i is missing when calling it, hence the variable is not found. 

```{r Section 4.4 Exercise 1}

my_variable <- 10
my_variable

```

Exercise # 2 - Tweak each of the following R commands so that they run correctly. 

```{r Section 4.4 Exercise 2}

library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)
filter(diamonds, carat > 3)

```

Section 5.2.4: #1, #3 and #4 only.

Exercise #1 - Find all flights that

Had an arrival delay of two or more hours
Flew to Houston (IAH or HOU)
Were operated by United, American, or Delta
Departed in summer (July, August, and September)
Arrived more than two hours late, but didn’t leave late
Were delayed by at least an hour, but made up over 30 minutes in flight
Departed between midnight and 6am (inclusive)


```{r Section 5.2.4 Exercise #1}

filter(flights, arr_delay >=2)
filter(flights, dest == "IAH" | dest == "HOU")
filter(flights, carrier == "AA" | dest == "DL")
filter(flights, month >= 7 & month <= 9)
filter(flights, arr_delay > 2 & dep_delay == 0)
filter(flights, dep_delay >= 1 & dep_delay-arr_delay > 0.5)
filter(flights, dep_time >= 0 & arr_time <= 600)

```

Exercise #3 - How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

>> There seems to be 8,255 flights without a departure time. 
Other variables missing for these flights are dep_delay, arr_time, arr_delay and air_time. These rows seem to represent cancelled flights.   



```{r Section 5.2.4 Exercise #3}

no_dep_time <- flights %>% filter(is.na(dep_time))


```

Exercise #4 - Why is NA ^ 0 not missing? Why is NA | TRUE not missing? Why is FALSE & NA not missing? Can you figure out the general rule? (NA * 0 is a tricky counterexample!)

>> Because NA represents an unknown value and almost any operation involving an unknown value will also be unknown. 

Section 5.4.1: #1 and #3 only.

Exercise #1 - 



