---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "Mario Casas Gonzalez"
date: "July 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


## RStudio and R Markdown (3 points)

1. Use markdown headers in your document to clearly separate each midterm question and add a table of contents to your document.

## The tidyverse packages (3 points)

#1. Can you name which package is associated with each task below?

Plotting - 'ggplot2' is the enhanced data visualization package we have been using for the most part. The 'plot' verb is included in Base R graphics.  

Data munging/wrangling - 'dplyr' is the package intended for data manipulation, providing a consistent set of verbs that help you solve the most common data manipulation challenges such as mutate, select, filter, summarise and arrange. Overall, 'tidyr' helps tidy the data. 

Reshaping (spreading and gathering) data - this is included in the 'tidyr' package, part of the 'tidyverse'. 

Importing/exporting data -

2. Now can you name two functions that you’ve used from each package that you listed above for these tasks?

Plotting -
Data munging/wrangling -
Reshaping data -
Importing/exporting data -

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(dplyr)
library(mdsr)
```



```{r pressure, echo=FALSE}

```

