---
title: "COMPSCIX 415.2 Homework 9/Final"
author: "Mario Casas Gonzalez"
date: "August 9, 2018"
output: 
  html_document:
    toc: TRUE
    theme: united 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)


```

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(dplyr)
library(mdsr)
library(broom)
library(readr)

```



Hyperlink to my Github repository: https://github.com/casasgmario/compscix-415-2-assignments.git

## Exercise 1 - Sampling Distributions, Functions and For Loops (10 points)

###Step 1

```{r Exercise1-Step1, echo=TRUE}

samp_size <- 100
samp_rate <- 1/10000

samp_fun <- function(samp_size, samp_rate) {
my_samp <- rexp(n = samp_size, rate = samp_rate)
samp_avg <- mean (my_samp)
samp_std_dev <- sd(my_samp)
stats <- list(samp_avg = samp_avg, samp_std_dev = samp_std_dev)
return(stats)
}

samp_fun(samp_size, samp_rate)



```


###Step 2

```{r Exercise1-Step2, echo=TRUE}
n <- 1000 
samp_size <- 50
samp_rate <- 1/10000
sample_means <- c(0)
sample_sds <- c(0)


for (i in 1:n) {
  samp_size <- 50
  samp_rate <- 1/10000
  my_list <- samp_fun(samp_size, samp_rate)
  sample_means[[i]] <- my_list$samp_avg
  sample_sds[[i]] <- my_list$samp_std_dev
}

```


###Step 3

```{r Exercise1-Step3, echo=TRUE}
sample_means_df <- as_data_frame(sample_means)
ggplot(sample_means_df, aes(x=value)) + geom_histogram()
my_sd <- sd(sample_means)
my_sd
theor_std_error <- my_sd/sqrt(samp_size)


```

###Step 4

```{r Exercise1-Step4, echo=TRUE}

n <- 1000 
samp_size <- 500
samp_rate <- 1/10000
sample_means <- c(0)
sample_sds <- c(0)


for (i in 1:n) {
  samp_size <- 50
  samp_rate <- 1/10000
  my_list <- samp_fun(samp_size, samp_rate)
  sample_means[[i]] <- my_list$samp_avg
  sample_sds[[i]] <- my_list$samp_std_dev
}

sample_means_df <- as_data_frame(sample_means)
ggplot(sample_means_df, aes(x=value)) + geom_histogram()
my_sd <- sd(sample_means)
my_sd
theor_std_error <- my_sd/sqrt(samp_size)

samp_size <- 5000

for (i in 1:n) {
  samp_size <- 50
  samp_rate <- 1/10000
  my_list <- samp_fun(samp_size, samp_rate)
  sample_means[[i]] <- my_list$samp_avg
  sample_sds[[i]] <- my_list$samp_std_dev
}

sample_means_df <- as_data_frame(sample_means)
ggplot(sample_means_df, aes(x=value)) + geom_histogram()
my_sd <- sd(sample_means)
my_sd
theor_std_error <- my_sd/sqrt(samp_size)

```

## Exercise 2 - Linear Regression (5 points)



• Interpret the coefficient on LotArea >> For every increase of 1 sq foot in the LotArea, the prediction of the model for the Sale Price increases by 1.453, when leaving the other 2 variables fixed (Overall Quality and External Quality)

• Interpret the coefficient on ExterQualGd >> For every increase of 1 unit in the ExterQualGd factor, the prediction of the model for the Sale Price decreases by 71529, when leaving the other 2 variables fixed (Lot Area and Overall Quality)


• Compare this model to the model we fit in HW 7 with GrLivArea, OverallQual, Neighborhood. Which is the better fitting model? >> We evaluate this with the adjusted R squared value, which in this case is 0.694 versus 0.783 on the HW 7 model, hence we can infer that the old HW 7 model was a better fit. 

```{r Exercise2, echo=TRUE}
train <- read_csv("~/Training/Berkeley/COMPSCI X415.2 - 002 Introduction to Data Science/Homeworks/Final Exam/train.csv")
(my_lm <- lm (SalePrice ~ LotArea + OverallQual + ExterQual, data=train))
tidy (my_lm)
glance(my_lm)


```



## Exercise 3 - AB Testing (5 points)

a. What proportion of visitors converted for each version of the webpage? > 4.15% on Version A and 10% on Version B. 
b. Perform the AB test in R. What is the p-value for the AB test (hypothesis test of proportions)? The p-value is 1.25388e-10. 


```{r Exercise3, echo=TRUE}
ab_test_data <- read_csv("~/Training/Berkeley/COMPSCI X415.2 - 002 Introduction to Data Science/Homeworks/Final Exam/ab_test_data.csv")
total_conversions <- ab_test_data %>% group_by (version) %>% summarise(total_conversions=sum(conversion))
total_conversions %>% mutate(conversion_rates=total_conversions/2000)
true_a <- 0.0415
true_b <-0.1
n_a <- 2000
n_b <- 2000
set.seed(10)
samp_a <- rbinom(n = 1, size = n_a, prob = true_a)
samp_b <- rbinom(n = 1, size = n_b, prob = true_b)
two_prop_test <- prop.test(c(samp_a, samp_b), c(2000, 2000))
two_prop_test$p.value


```